Data_visualization

### 2018-05-03 Rmd/Data_visualization.Rmd
Ovules boxplot Markdown

## Ovules

```{r, warning=FALSE, echo=FALSE}
#load libraries

library(ggplot2)
library(Hmisc)
library(Formula)
#load data
d<-read.csv("Data/Ovules.csv", sep=";")

>>>>

# Ovules per family, **Convolvulaceae is constant 4 or 6**

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
#load libraries

library(ggplot2)
library(Hmisc)
library(Formula)
#load data

par(mfrow=c(2,1))

d<-read.csv("Data/Ovules.csv", sep=";")
